
\documentclass[botnum, nobox]{unmeethesis}

\usepackage{float}                 % to force figure placement with "H"

\usepackage{amsmath}               % to show matrices \begin{bmatrix}

\usepackage{blindtext}             % Sometimes I get the black boxes seen here http://tex.stackexchange.com/a/111956
\usepackage{multirow}              % for the table
\usepackage{color, colortbl}
\definecolor{LightGray}{gray}{.9}  % for table rows
\usepackage{relsize}
\usepackage{graphicx}
\usepackage{caption}     % for multi figure figures
\usepackage{subcaption}  % for multi figure figures

\usepackage{listings}              % for appendix of python code

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  basicstyle=\scriptsize,          % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=t,                    % sets the caption-position to bottom
  commentstyle=\color{mygreen},    % comment style
  deletekeywords={...},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=single,	                   % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{blue},       % keyword style
  language=Python,                 % the language of the code
  otherkeywords={*,...},           % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mymauve},     % string literal style
  tabsize=2,	                     % sets default tabsize to 2 spaces
  title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
}

\captionsetup[table]{skip=0pt} % reduce caption space between tables and caption

\begin{document} % _____________________________________________ Begin Document

\frontmatter

% Uncomment the next command if you see weird paragraph spacing:
% That is, if you see paragraphs float with lots of white space
% in between them:
\setlength{\parskip}{0.30cm}


\title{Mesh Addition Based on the Depth Image\\(MABDI)}

\author{Lucas E. Chavez}

\degreesubject{M.S., Mechanical Engineering}

\degree{Master of Science \\ Mechanical Engineering}

\documenttype{Thesis}

\previousdegrees{B.S., Mechanical Engineering \\
New Mexico Institute of Mining and Technology, 2009}

\date{December, 2016}

\maketitle

% \begin{dedication}
%    To my parents, Albert II and Gladys, for their support,
%    encouragement and the Corvette they're giving me for graduation. \\[3ex]
%    ``A bird in hand is worth two in the bush''
%          -- Anonymous
% \end{dedication}

\begin{acknowledgments}
   \vspace{1.1in}
   This work was supported in part by Sandia National Laboratories under Purchase
   Order: 1179196 and  NSF grant OISE \#1131305.
\end{acknowledgments}

\maketitleabstract %(required even though there's no abstract title anymore)


\begin{abstract}
  \vspace{-10pt}
  Many robotic applications utilize a detailed map of the world and the
  algorithm used to produce such a map must take into consideration real-world
  constraints such as computational and memory costs. Traditional mesh-based
  environmental mapping algorithms receive data from the sensor, create a mesh
  surface from the data, and then append the surface to a growing global mesh.
  These algorithms do not provide a computationally efficient mechanism for
  reducing redundancies in the global mesh. MABDI is able to leverage the
  knowledge contained in the global mesh to find the difference between what we
  expect our sensor to see and what the sensor is actually seeing. This
  difference between expected and actual allows MABDI to classify the data from
  the sensor as either data from a novel part of the environment or data from a
  part of the environment we have already seen before. Using only the novel
  data, a surface is created and appended to the global mesh. MABDI's
  algorithmic design identifies redundant information and removes it
  \emph{before} it is added to the global mesh. This reduces the amount of
  memory needed to represent the mesh and also lessens the computational needs
  to generate mesh elements from the data.
\clearpage %(required for 1-page abstract)
\end{abstract}

\tableofcontents
\pagebreak

\mainmatter % _____________________________________________________ Main Matter

\input{c_introduction}

\input{c_related_works}

\input{c_approach}

\input{c_experimental_setup}

\input{c_results}

\input{c_conclusion}


\appendix % __________________________________________________________ Appendix

\chapter{MABDI code}
\label{appendix:mabdi_code}
\section{FilterDepthImage.py}
\lstinputlisting[language=Python, title=FilterDepthImage.py]{code/FilterDepthImage.py}
\section{FilterClassifier.py}
\lstinputlisting[language=Python, title=FilterClassifier.py]{code/FilterClassifier.py}
\section{FilterDepthImageToSurface.py}
\lstinputlisting[language=Python, title=FilterDepthImageToSurface.py]{code/FilterDepthImageToSurface.py}
\section{FilterWorldMesh.py}
\lstinputlisting[language=Python, title=FilterWorldMesh.py]{code/FilterWorldMesh.py}


\bibliographystyle{IEEEtran}
\bibliography{bibliography}

\end{document}
